### 2014-11-20 Paper1/paper1.tex
Does not matter, stylistic change

\subsection*{Indices of variance-based sensitivity}
To ensure a properly spaced and efficient evaluation of sensivity, we employed Sobol-distributed matrices, generated using MATLAB's \textit{sobolset()} function and converted to parameter distributions (see Table~\ref{tab:parameters}) using inverse cumulative probability density. Nominal parameters values were mostly taken from taken Dempster \cite{dempster1955space} and Burdet et al. \cite{burdet2006stability} with typical values where subject-specific parameters (height and weight) and direct where necessary (force sensor noise and drift). Standard deviations reflect expected variation in repeated measurement (ie. height and weight) or measured variance (ie. trial-to-trial variation in sensor noise or uncertainty in mass ratios reported by Dempster \cite{dempster1955space}). Distributions were clamped to the range of $\pm3$ standard deviations in order to limit parameters to a realistic range. Combinations and calculations were made as prescribed by Saltelli et al. \cite{saltelli2010variance} to arrive at direct and total sensitivity indices.

@@

\pagebreak
\section*{Figures and Figure Legends}
%\begin{figure}[!ht]
%\begin{center}
%%\includegraphics[width=4in]{figure_name.2.eps}
%\end{center}
%\caption{
%{\bf Bold the first sentence.}  Rest of figure 2  caption.  Caption 
%should be left justified, as specified by the options to the caption 
%package.
%}
%\label{Figure_label}
%\end{figure}
\begin{figure}[!ht]
\begin{center}
\includegraphics[width=6in]{fig1.png}
\end{center}
\caption{
{\bf Simulated data illustrating tautology of extraction across pulse and filtered Gaussian noise disturbance types.} Intent is modeled as a minimum jerk, 5th order polynomial. Forces experienced are combined with intent via Burdet et al.'s \cite{burdet2006stability} model to produce the simulated arm trajectory. Extraction to recover intention from arm and force trajectory follows. Parameter errors are introduced into the extraction and varied according to Table 1 to estimate sensitivity. Examining the distribution of trajectories from this analysis reveals that this sensitivity is not uniformly distributed throughout a reach.
}
\label{fig:synthetic}
\end{figure}

>>>>

\subsection*{Indices of variance-based sensitivity}
To ensure a properly spaced and efficient evaluation of sensivity, we employed Sobol-distributed matrices, generated using MATLAB's \textit{sobolset()} function and converted to parameter distributions (see Table~\ref{tab:parameters}) using inverse cumulative probability density. Nominal parameters values were mostly taken from taken Dempster \cite{dempster1955space} and Burdet et al. \cite{burdet2006stability} with typical values where subject-specific parameters (height and weight) and direct where necessary (force sensor noise and drift). Standard deviations reflect expected variation in repeated measurement (ie. height and weight) or measured variance (ie. trial-to-trial variation in sensor noise or uncertainty in mass ratios reported by Dempster \cite{dempster1955space}). Distributions were clamped to the range of $\pm 3$ standard deviations in order to limit parameters to a realistic range. Combinations and calculations were made as prescribed by Saltelli et al. \cite{saltelli2010variance} to arrive at direct and total sensitivity indices.

@@

\pagebreak
\section*{Figures and Figure Legends}
%\begin{figure}[!ht]
%\begin{center}
%%\includegraphics[width=4in]{figure_name.2.eps}
%\end{center}
%\caption{
%{\bf Bold the first sentence.}  Rest of figure 2  caption.  Caption 
%should be left justified, as specified by the options to the caption 
%package.
%}
%\label{Figure_label}
%\end{figure}
\begin{figure}[!ht]
\begin{center}
\includegraphics[width=6in]{fig1.png}
\end{center}
\caption{
{\bf Simulated data illustrating tautology of extraction across pulse and filtered Gaussian noise disturbance types.} Intent is modeled as a minimum jerk, 5th order polynomial. Forces experienced are combined with intent via Burdet et al.'s \cite{burdet2006stability} model to produce the simulated arm trajectory. Extraction to recover intention from arm and force trajectory follows. Parameter errors are introduced into the extraction and varied according to Table 1 to estimate sensitivity. Examining the distribution of deviation in trajectories from this analysis reveals that sensitivity is not uniformly distributed throughout a reach.
}
\label{fig:synthetic}
\end{figure}
